\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
  {Master of Science in Computer Science,}{UQAM | Université du Québec À Montréal}{\WorkLocation{Montréal, Qc, Ca}}
    {\WorkPeriod{Sep 2016}{\break Dec 2018}}
    \resumeItemListStart
      \renewcommand{\labelitemii}{\raisebox{.39cm}{$\bullet$}}
      \resumeItem{Main reseach project}{Android : Automatic detection of presentation layer architectural
      design patterns (MVC, MVP, MVVM) in Android apps through bytecode analysis. A tooled approach and an 
      empirical study. Source: \underline{\url{https://github.com/AymenDaoudi/Rimaz}}}
      \renewcommand{\labelitemii}{\raisebox{.15cm}{$\bullet$}}
      \resumeItem{Research Papers}{Published a research paper \textbf{"\textit{\underline{\href{https://dl.acm.org/citation.cfm?id=3297447&dl=ACM&coll=DL}{An Exploratory Study of MVC-based Architectural Patterns in
      Android Apps}}}"} to the international ACM SAC Conference (SAC’19).}
      \renewcommand{\labelitemii}{\raisebox{.27cm}{$\bullet$}}
      \resumeItem{Research Project}{Participated in a research project with the company Savoir Faire Linux. Proposing 
      solutions to assess P2P VOIP apps (such as Skype, Jami (prev. Ring) and Tox) software quality for 
      performance and energy consumption.}
      \renewcommand{\labelitemii}{\raisebox{.05cm}{$\bullet$}}
      \resumeItem{Supervising}{Supervising interns building Xamarin applications.}
      \renewcommand{\labelitemii}{\raisebox{0.05cm}{$\bullet$}}
      \resumeItem{Teaching}{Giving Java courses and workshops for Bachelor students.}
    \resumeItemListEnd
  \resumeSubheading
  {Master degree in computer science (Information systems),}{ESI | Ecole Nationale Supérieure d’Informatique}{\WorkLocation{Algiers, Algeria}}
  {\WorkPeriod{Sep 2007}{\break Juin 2014}}
    \resumeItemListStart
    \renewcommand{\labelitemii}{\raisebox{.24cm}{$\bullet$}}
      \resumeItem{Final Project}{Ranking web pages using Google’s PageRank algorithm: study, modeling, implementation
      and simulation. Source: \underline{\url{https://github.com/SamTheDev/PageRank-Analyzer}}}
  \resumeItemListEnd
  \resumeSubheading
  {High school diploma (baccalauréat)}{Lycée Chihani Bachir}{\WorkLocation{Khenchela, Algeria}}
  {\WorkPeriod{2004}{ 2007}}
\resumeSubHeadingListEnd