\section{Employment}
  % Define default environment command
  \renewcommand{\environment}[1]{
    \vspace{-6pt}
    \item[{$\bullet$}]
    \fcolorbox{white}{white}{
      \parbox{0.82\textwidth}{
        \roboto{\textbf{Environment:}}
        \roboto{\footnotesize #1}
      }}
      \vspace{0pt}
  }
  \resumeSubHeadingListStart
  \resumeSubheading
  {Senior Software Engineer,}{Stealth Project}{\WorkLocation{Montreal.}}
  {\WorkPeriod{January 2024}{\break \textbf{Present}}}
    \resumeItemListStart
      \renewcommand{\resumeItem}[2]{
        \vspace{-5pt}
        \item [\raisebox{1ex}{$\bullet$}]\fcolorbox{white}{white}{
          \parbox{0.82\textwidth}{
            \roboto{\textbf{#1:}}
            \roboto{\footnotesize #2}
          }
        }
        \vspace{0pt}
      }
      \resumeItem{Viral genomic analyses}{Building an AI/ML platform for viral genome taxonomy analysis with features including:}
      \begin{itemize}
        \resumeSubItem{~~}{Virus, infection type, and subtype identification through DNA/RNA analysis.}
        \resumeSubItem{~~}{Geographic origin prediction for sequences like HIV.}
      \end{itemize}
      \renewcommand{\resumeItem}[2]{
        \vspace{-5pt}
        \item [$\bullet$]\fcolorbox{white}{white}{
          \parbox{0.82\textwidth}{
            \roboto{\textbf{#1:}}
            \roboto{\footnotesize #2}
          }
        }
        \vspace{0pt}
      }
      \resumeItem{Management}{}
      \begin{itemize}
        \resumeSubItem{~~}{Led a team of five data scientists, engineers, and software developers.}
        \resumeSubItem{~~}{Managed sprint planning, task breakdown, and team coordination.}
        \resumeSubItem{~~}{Facilitated cross-functional collaboration and alignment.}
      \end{itemize}
      \resumeItem{Software Development and architecture}{}
      \begin{itemize}
        \resumeSubItem{~~}{Developed APIs for analyzing multi-gigabyte viral sequence \href{https://www.ncbi.nlm.nih.gov/genbank/fastaformat/}{fasta} files.}
        \resumeSubItem{~~}{Built a Flutter web application for displaying viral sequences and analysis results.}
        \resumeSubItem{~~}{Managed CI/CD pipelines and ETL processes in Python.}
      \end{itemize}
      \environment{Microservices, REST, Python(Django), C\#(.NET8), Dart(Flutter), Docker, Azure, Azure DevOps, Postgres, MongoDb.}
    \resumeItemListEnd
    \resumeSubheading
    {Senior Software Engineer,}{Divisions Maintenance Group}{\WorkLocation{(USA) Remote.}}
    {\WorkPeriod{April 2022}{\break \textbf{Present}}}
      \resumeItemListStart
        \resumeItem{Software Development}{}
        \begin{itemize}          
          \resumeSubItem{~~}{Developed microservices and APIs for \href{https://divisionsmg.com/dmg-pro/}{DMG Pro}, a platform connecting maintenance providers with U.S. job opportunities.}
          \renewcommand{\resumeSubItem}[2]{
            \vspace{-6pt}
            \setlength{\itemindent}{-40pt}
            \item[\textendash] % Raise the dash slightly using \raisebox
              \fcolorbox{white}{white}{
              \parbox{0.82\textwidth}{
                \roboto{\textbf{\footnotesize #1}}{\hspace{-11pt}\footnotesize #2}
              }} 
            \vspace{0pt}
          }
          \resumeSubItem{~~}{Promoted software best practices through code reviews, documentation, and technical articles.}
          \resumeSubItem{~~}{Implemented CI/CD pipelines using Docker and Kubernetes.}
        \end{itemize}
        \resumeItem {Design and architecture}{}
        \begin{itemize}
          \resumeSubItem{~~}{Built a dynamic validation system for data types (jobs, addresses, components).}
          \resumeSubItem{~~}{Created a template engine for marketing teams to manage communications.}
          \resumeSubItem{~~}{Developed a CLI tool to scaffold C\#/.NET APIs and components.}
          \resumeSubItem{~~}{Helped teams migrate from Git flows to Microsoft Release Flow, improving efficiency and reducing bottlenecks.}
          \resumeSubItem{~~}{Implemented automated Semantic Versioning (SemVer) across projects.}
          \resumeSubItem{~~}{Redesigned APIs using DDD and Onion architecture principles.}
          \resumeSubItem{~~}{Built a local QA test environment using \textbf{Docker Compose}, \textbf{Grafana}, \textbf{Loki} and \textbf{Prometheus} to reduce costs and improve independence.}

          \resumeSubItem{~~}{Enhanced integration testing using Docker for local environments and CI pipelines.}
        \end{itemize}
        \renewcommand{\environment}[1]{
          \vspace{-6pt}
          \item[\raisebox{1.2ex}{$\bullet$}]
          \fcolorbox{white}{white}{
            \parbox{0.82\textwidth}{
              \roboto{\textbf{Environment:}}
              \roboto{\footnotesize #1}
            }}
            \vspace{0pt}
        }
        \environment{Microservices, gRPC, REST, Python(Django), TypeScript(NestJS), C\#(.NET8), Unit \& Integration Testing, Postgres, MongoDb, Elasticsearch, Kafka, Docker, Kubernetes, Github, AWS.}
      \resumeItemListEnd
    \resumeSubheading
    {Backend Software developer}{AddEnergie}{\WorkLocation{Montréal, Qc, Ca.}}
    {\WorkPeriod{January 2022}{\break April 2022}}
      \resumeItemListStart
        \resumeItem
        {Electric charging stations}{Building APIs and services for AddEnergie's network of electric car charging stations.}
        \environment{Microservices, C\#(.Net core), SQLServer, MongoDb, Docker, Kafka, Kubernetes, Azure, Azure DevOps.}
      \resumeItemListEnd

    \resumeSubheading
    {Full stack Software developer,}{Lloyd's Register OneOcean (ex. MarinePress)}{\WorkLocation{Montréal, Qc, Ca.}}
    {\WorkPeriod{March 2020}{\break January 2022}}
      \resumeItemListStart
        \renewcommand{\resumeItem}[2]{
          \vspace{-5pt}
          \item [\raisebox{1ex}{$\bullet$}]\fcolorbox{white}{white}{
            \parbox{0.82\textwidth}{
              \roboto{\textbf{#1:}}
              \roboto{\small #2}
            }
          }
          \vspace{0pt}
        }
        \resumeItem
        {OneOcean} {Developed and maintained backend and frontend components of OneOcean, a maritime navigation software that integrates compliance, performance, and safety tools. Key contributions:}
        \begin{itemize}
          \resumeSubItem{~~}{Implemented CI/CD pipelines and managed DevOps operations.}
          \resumeSubItem{~~}{Authored RFCs, documentation, \href{https://medium.com/oneoceangroup/publishing-and-consuming-debugging-symbols-for-net-core-library-d0e831f5862}{technical articles} and presentations.}
        \end{itemize}
        \renewcommand{\environment}[1]{
          \vspace{-6pt}
          \item[\raisebox{1.2ex}{$\bullet$}]
          \fcolorbox{white}{white}{
            \parbox{0.82\textwidth}{
              \roboto{\textbf{Environment:}}
              \roboto{\footnotesize #1}
            }}
            \vspace{0pt}
        }
        \environment{Microservices, C\#(.Net core), Python(Django + FastAPI), TypeScript(Angular), Unit \& Integration Testing, SQLServer, MongoDb, Docker, Kafka, Kubernetes, Azure, Azure DevOps.}
      \resumeItemListEnd

    \resumeSubheading
    {Full stack Software developer,}{Stratec global}{\WorkLocation{Montréal, Qc, Ca.}}
    {\WorkPeriod{Jan 2019}{\break Mar 2020}}
      \resumeItemListStart        
        \resumeItem
        {ITMatters} {A platform for managing financial policies, agencies and insurances. Key responsibilities include:}
        \begin{itemize}
          \resumeSubItem{~~}{Analyzed customer requirements and gathered business rules.}
          \resumeSubItem{~~}{Developed the backend for the main web application and a cross-platform mobile app.}
          \resumeSubItem{~~}{Contributed to the development of a Xamarin cross-platform mobile application.}
          \resumeSubItem{~~}{Implemented CI/CD pipelines and handled various DevOps tasks.}
        \end{itemize}
        \environment{C\#(.Net core), Unit \& Integration Testing, Xamarin, MVVM, Rx, SQLServer, Azure, Azure DevOps, AWS.}
      \resumeItemListEnd

    \pagebreak

    \resumeSubheading
    {Research assistant,}{UQAM | Université du Québec À Montréal}{\WorkLocation{Montréal, Qc, Ca.}}
    {\WorkPeriod{Sep 2016}{\break Dec 2018}}
      \resumeItemListStart
        \renewcommand{\resumeItem}[2]{
          \vspace{-5pt}
          \item [\raisebox{1.3ex}{$\bullet$}]\fcolorbox{white}{white}{
            \parbox{0.82\textwidth}{
              \roboto{\textbf{#1:}}
              \roboto{\footnotesize #2}
            }
          }
          \vspace{0pt}
        }
        \resumeItem{Main reseach project}{Automatic detection of architectural design patterns (MVC, MVP, MVVM) in Android applications. Key achivements include:}
        \begin{itemize}
          \renewcommand{\resumeSubItem}[2]{
            \vspace{-6pt}
            \setlength{\itemindent}{-40pt}
            \item[\raisebox{0.2ex}{\textendash}] % Raise the dash slightly using \raisebox
              \fcolorbox{white}{white}{
              \parbox{0.82\textwidth}{
                \roboto{\textbf{\scriptsize #1}}{\hspace{-11pt}\footnotesize #2}
              }} 
            \vspace{0pt}
          }
          \resumeSubItem{~~}{Developed a tool for static analysis on Android apps bytecode, source: \underline{\url{https://github.com/AymenDaoudi/Rimaz}}.}
          \renewcommand{\resumeSubItem}[2]{
            \vspace{-6pt}
            \setlength{\itemindent}{-40pt}
            \item[{\textendash}] % Raise the dash slightly using \raisebox
              \fcolorbox{white}{white}{
              \parbox{0.82\textwidth}{
                \roboto{\textbf{\scriptsize #1}}{\hspace{-10pt}\footnotesize #2}
              }} 
            \vspace{0pt}
          }
          \resumeSubItem{~~}{Conducted bytecode exploration and empirical analysis on thousands of Android applications using the developed tool.}        
          \resumeSubItem{~~}{Authored and published the research paper \textbf{"\textit{\underline{\href{https://dl.acm.org/citation.cfm?id=3297447&dl=ACM&coll=DL}{An Exploratory Study of MVC-based Architectural Patterns in
          Android Apps}}}"} at (SAC'19).}
        \end{itemize}
        \resumeItem
         {CRIM | Computer Research Institute of Montreal}
         {Plugin development and a programming language integration in Eclipse for writing flight simulator test cases.}
        \resumeItem{Savoir Faire Linux}
          {Conducted a comparative study on the performance and energy consumption of VOIP serverless applications. Key activities included:}
          \begin{itemize}
            \resumeSubItem{~~}{Assessed performance and energy consumption of Jami (ex. Ring), Skype, and Tox, focusing on CPU, memory, and bandwidth usage.}
            \renewcommand{\resumeSubItem}[2]{
              \vspace{-6pt}
              \setlength{\itemindent}{-40pt}
              \item[{\textendash}] % Raise the dash slightly using \raisebox
                \fcolorbox{white}{white}{
                \parbox{0.82\textwidth}{
                  \roboto{\textbf{\scriptsize #1}}{\hspace{-11pt}\footnotesize #2}
                }} 
              \vspace{0pt}
            }
            \resumeSubItem{~~}{Benchmarked and compared the results of the three applications.}
            \resumeSubItem{~~}{Developed \textbf{Netraf}, a Linux tool for monitoring bandwidth usage. Source: \underline{\url{https://github.com/AymenDaoudi/NeTraf}}.}
          \end{itemize}
        
      \resumeItemListEnd

    \resumeSubheading
    {Consultant,}{Novasup}{\WorkLocation{Algiers, Algeria}}{\WorkPeriod{Feb 2016}{\break Aug 2016}}
      \resumeItemListStart
        \renewcommand{\resumeItem}[2]{
          \vspace{-5pt}
          \item [{$\bullet$}]\fcolorbox{white}{white}{
            \parbox{0.82\textwidth}{
              \roboto{\textbf{#1:}}
              \roboto{\footnotesize #2}
            }
          }
          \vspace{0pt}
        }
        \resumeItem{Windows apps}
          {Developed, and published mobile apps for several Algerian newspapers on the Windows Store.}
        \environment{Visual Studio 2015, C\#, UWP, MVVM, ASP.Net core, Rest, Nunit, Entity Framework, SQLite.}
      \resumeItemListEnd
    \resumeSubheading
    {Experience Technical Evangelist Developer (Internship),}{Microsoft}{\WorkLocation{Algiers, Algeria}}{\WorkPeriod{Dec 2015}{\break Aug 2016}}
      \resumeItemListStart
        \resumeItem{Microsoft Azure}{Collaborated with ISVs and startups to integrate Microsoft Azure solutions.}
        \environment{C\#, UWP, Entity Framework, Rest, Unit \& Integration Testing, SQLite, Microsoft Azure.}
      \resumeItemListEnd
      \resumeSubheading
      {.Net developer,}{HydraPharm Group}{\WorkLocation{Algiers, Algeria}}{\WorkPeriod{Jan 2014}{\break Dec 2015}}
      \resumeItemListStart
        \renewcommand{\resumeItem}[2]{
          \vspace{-5pt}
          \item [\raisebox{1.3ex}{$\bullet$}]\fcolorbox{white}{white}{
            \parbox{0.82\textwidth}{
              \roboto{\textbf{#1:}}
              \roboto{\footnotesize #2}
            }
          }
          \vspace{0pt}
        }
        \resumeItem{Software development}{Developed internal software for reporting and sales services.}
        \environment{C\#, WPF, MVVM, WCF, Unit \& Integration Testing, DevExpress, SQLServer 2008.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
